\documentclass{article}
\input{../../header.tex}
\begin{document}
Let $p : \mathbf{E}\to \mathbf{B}$ be a
fibration of 2-categories. What exactly is the claim?

Let $\mathcal{J} : \mathbf{A}\to \mathbf{E}$ be a (strict!)
2-functor and let $P : \mathbf{A}\to \mathbf{Cat}$ be a
(strict!) 2-functor.

Remember that there are two distinct definitions of cone.

A strict cone would be a family of functors
$P(e) \Rightarrow \mathbf{Hom}_{\mathbf{Cat}}(\mathcal{J}(-), e)$,
indexed by $e \in \mathbf{E}$, forming a strict natural
transformation, i.e., the functor diagrams commute on the nose.

A pseudocone is defined to be a pseudonatural transformation,
i.e., all the squares commute up to (coherent) natural isomorphism.

I ran into a problem. What is my problem?
Something is false. What was it?

The following theorem is, I think, false.

\begin{theorem}
  Let $p: \mathbf{E}\to \mathbf{B}$ be a (strict) 2-fibration.
  Let $\mathbb{A}$ be a double category.
  There are double functor categories
  $\mathbb{Q}(\mathbf{E})^{\mathbb{A}}$,
  $\mathbb{Q}(\mathbf{B})^{\mathbb{A}}$,
  and $p$ induces a double functor between them by
  postcomposition. Restricting to $\mathbf{H}(p)$
  (i.e., only caring about the behavior of $p$
  on horizontal 1-cells) induces a fibration of 2-categories.
\end{theorem}

I no longer think this is true, without further
assumptions on the categories involved.
The problem is that the pullback of a natural transformation
along a modification may not be strictly natural, in general.
It will only be ``pseudonatural.'' And the concept
of a pseudonatural transformation between double functors
goes beyond what we are prepared to handle.

Recall that $\mathbf{H}(\mathbb{Q}(\mathbf{E})^{\mathbb{A}})$
consists of
\begin{itemize}
\item objects: pseudo double functors $\mathbb{A}\to \mathbf{E}$
\item 1-cells: horizontal natural transformations
  (these are required to commute strictly)
\item 2-cells: modifications, etc.
\end{itemize}

So, let us go back to the drawing board.

\section{What we have to work with}
Let $p : \mathbf{E}\to \mathbf{B}$ be a (strict) 2-fibration between
2-categories. Let $\mathbb{A}$ be a (strict) double category.
Let $F : \mathbb{A}\to \mathbf{E}$.

For each $e$ there is a category $\operatorname{Cone}(c, F)$
whose \textit{objects} are (strict) horizontal natural transformations $c\Rightarrow F$
and whose objects are modifications between them.

then for fixed $e$, there is a correspondence between
\begin{itemize}
\item strict, 
\end{itemize}



\end{document}
